Naming Anonymous JavaScript Functions

### 2011-04-12 trunk/papers/splash-wavefront2011/sigplanconf-template.tex
add examples for cases 10 11

If the called-function is assigned to a variable or object property, then we have a version of one of the other cases in Table~\ref{function-types}. The difference here is that we can tell from static analysis that the assignment will use the return value of the function, not the function object itself. But for naming purposes the key information will be the assignment target.

@@

\subsection{Case 10: Function Property is Accessed}
This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or an argument function to {\small\texttt{Function}} object prototype is called.

@@

Although this category only includes 2\% of nameless function, proper naming of functions in this class is important. Many constructors are built using this form and therefore the names of these functions appear in object summaries.

@@

The particular symbols we use may be refined with more experience in how developers respond to them. Our intuition is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier. For example, the function on line 9 of Fig.~\ref{fig:js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.

>>>>

If the called-function is assigned to a variable or object property, then we have a version of one of the other cases in Table~\ref{table:function-types}. The difference here is that we can tell from static analysis that the assignment will use the return value of the function, not the function object itself. But for naming purposes the key information will be the assignment target.

@@

\subsection{Case 10: Function Property is Accessed}
In this unusual case a property of the function is accessed directly from the function body. This case usually happens one of the predefined functions of function object (i.e., {\small\texttt{call, apply, bind}}) or when the predefined functions are augmented by adding to {\small\texttt{Function}} prototype.  Here is an example, from ExtJS, reformatted for display here:
\begin{verbatim}
setVisible : function(v, a, d, c, e){
    if(v){
        this.showAction();
    }
    if(a && v){
        var cb = function(){
            this.sync(true);
            if(c){
                c();
            }
        }.createDelegate(this);
   }
   // .....
}
\end{verbatim}
The inner function body is not used directly, but the result of \verb|createDelegate| is assigned to \verb|cb|. The most valuable information here is the variable name \verb|cb|, followed by the \verb|createDelegate| function name.  This example also illustrates that automatic naming could have an effect on developers coding style:  giving a longer name for \verb|cb| would give better names in development tools but currently developers have limited expectations that tools will show such information.

@@

In this case the function body appears in a return statement of another function body. Although this category only includes 2\% of nameless function, proper naming of functions in this class is important. Many constructors are built using this form and therefore the names of these functions appear in object summaries.    Clearly the name of these returned functions is almost the same as the name of the functions that define them. For example, in Fig.~\ref{fig:registerWin} a developer might pick names like \verb|registerWinOnIE| and \verb|registerWinNotOnIE| for the functions returned by the Dojo function \verb|registerWin|.
\begin{figure*}[htbp]
\begin{verbatim}
registerWin: function(targetWindow, effectiveNode){
  // ...
  if(doc){
    if(dojo.isIE){
      ....
      return function(){
        doc.detachEvent('onmousedown', mousedownListener);
        doc.detachEvent('onactivate', activateListener);
        doc.detachEvent('ondeactivate', deactivateListener);
        doc = null;    // prevent memory leak (apparent circular reference via closure)
      };
    }else{
      ....
      return function(){
        doc.removeEventListener('mousedown', mousedownListener, true);
        doc.removeEventListener('focus', focusListener, true);
        doc.removeEventListener('blur', blurListener, true);
        doc = null;    // prevent memory leak (apparent circular reference via closure)
      };
    }
  }
},
\end{verbatim}
\label{fig:registerWin}
\caption{An example of a function body in a return statement, case 11 of Table~\ref{table:function-types}  adapted from the Dojo project code}
\end{figure*}

@@

The particular symbols we use may be refined with more experience in how developers respond to them. Our intuition is that these extra symbols need to be visually compact because their purpose is to adjust the developers expectation for the identifier. For example, the function on line 9 of Fig.~\ref{js-code} is named \texttt{main<} but the developer may only key on the word \texttt{main} to recall the function body.
